Notes on the Godunov Step in {\tt MAESTRO}

### 2008-04-15 docs/Godunov_notes/paper.tex
added text about the velocity forcing
more cleanup in the umac section

\def\eb    {{\bf e}}
\def\ib    {{\bf i}}
\def\Ub    {{\bf U}}
\def\er    {{\bf e}_r}

@@

\section{Computing $\Ub^{\trans}$}
In {\tt advance\_premac.f90}, we call the function {\tt mkutrans}, which computes the edge-centered transverse velocities, $\Ubt^{\trans}$.  These transverse velocities do not contain $w_0$, so immediately following the call to {\tt mkutrans}, we call {\tt addw0} to compute $\Ub^{\trans}$ from $\Ubt^{\trans}$.  We will only compute the normal component of velocity at each face.\\

@@

For the x-faces, the extrapolation is as follows:
\begin{eqnarray}
u_L &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{h}u_{\ib-\eb_x}^n\right)\Delta_x u_{\ib-\eb_x}^n, \\
u_R &=& u_{\ib}^n - \left(\half + \frac{\dt}{h}u_{\ib}^n\right)\Delta_x u_{\ib}^n.
\end{eqnarray}
We pick the final edge states using a Riemann solver:
\begin{equation}
u^{\trans}_{\ib-\half\eb_x} =
\begin{cases}
0, & (u_L \le 0 ~ {\rm AND} ~ u_R \ge 0) ~ {\rm OR} ~ |u_L + u_R| < \epsilon, \\
u_L, & u_L + u_R > 0, \\
u_R, & u_L + u_R < 0, \\
\end{cases}
\end{equation}
For the radial faces, we must include the radial derivative terms proportional to $w_0$ and $(\Ubt\cdot\eb_r) = \wt$.  The term proportional to $w_0$ is included by using $w$ rather than $\wt$ as the advection speed.  The term proportional to $\wt$ is an additional term:
\begin{eqnarray}
\wt_L &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{h}w_{\ib-\eb_r}^n\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}\wt_{\ib-\eb_r}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib-\eb_r},\label{Radial utrans_L} \\
\wt_R &=& \wt_{\ib}^n + \left(\half - \frac{\dt}{h}w_{\ib}^n\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}\wt_{\ib}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib}.\label{Radial utrans_R}
\end{eqnarray}
The total radial velocity is defined as:
\begin{equation}
w_{\ib}^n = \wt_{\ib}^n + \frac{w_{0,r+\half}+w_{0,r-\half}}{2}.\label{Total Radial Velocity}
\end{equation}
The spatial derivatives of $w_0$ are given by the two-point centered difference:
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)_{\ib} = \frac{w_{0,r+\half}-w_{0,r-\half}}{h}.\label{Radial Derivative of w_0}
\end{equation}
We pick the final edge states using:
\begin{equation}
\wt^{\trans}_{\ib-\half\eb_r} =
\begin{cases}
0, & (w_L \le 0 ~ {\rm AND} ~ w_R \ge 0) ~ {\rm OR} ~ |w_L + w_R| < \epsilon, \\
\wt_L, & w_L + w_R > 0, \\
\wt_R, & w_L + w_R < 0, \\
\end{cases}
\end{equation}
where $w_L = \wt_L + w_{0,r-\half}$ and $w_R = \wt_R + w_{0,r-\half}$.  Finally, we call {\tt addw0} to compute $\wt^{\trans}$ from $w^{\trans}.$
\subsection{3D Cartesian Case}
For the rest of this paper, for 3D Cartesian problems, $\Ub = (u,v,w)$ and $\Ubt = (u,v,\wt)$.  We will use the shorthand $\ib = (i,j,r)$.\\

@@

For spherical problems, we first construct $\Ub$ by mapping $w_0$ onto a Cartesian array and adding it to $\Ubt$.  This is a spherical generalization of equation (\ref{Total Radial Velocity}).  We also map $\partial w_0/\partial r$ onto a Cartesian array.  This is a spherical generalization of equation (\ref{Radial Derivative of w_0}).  Then we use an extrapolation analogous to equations equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}).  For example, for x-faces:
\begin{eqnarray}
\ut_L &=& \ut_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{h}u_{\ib-\eb_x}^n\right)\Delta_x\ut_{\ib-\eb_x}^n + \frac{\dt}{2}\left[(\Ubt^n\cdot\eb_r)\left(\frac{\partial w_0}{\partial r}\right)(\eb_r\cdot\eb_x)\right]_{\ib-\eb_x}, \\
\ut_R &=& \ut_{\ib}^n + \left(\half - \frac{\dt}{h}u_{\ib}^n\right)\Delta_x\ut_{\ib}^n + \frac{\dt}{2}\left[(\Ubt^n\cdot\eb_r)\left(\frac{\partial w_0}{\partial r}\right)(\eb_r\cdot\eb_x)\right]_{\ib}.
\end{eqnarray}
Then, we use the same Riemann solver as the Cartesian case to obtain $\ut^{\trans}$.  To compute $\vt^{\trans}$ or $\wt^{\trans}$, simply replace all instaces of $\ut$ with $\vt$ (or $\wt$) and all instaces of $x$ with $y$ (or $z$).  Finally, we call {\tt addw0} to compute $\Ubt^{\trans}$ fromm $\Ub^{\trans}$.
\section{Computing $\Ub^{\mac}$}
In {\tt advance\_premac.f90}, we call {\tt make\_edge\_state} to compute $\Ubt^{\mac}$.
\subsection{2D Cartesian Case}
Here are the steps to create $u^{\mac}$ for 2D Cartesian problems.  First, we need to compute a time-centered $u$ at transverse faces using a 1D Taylor series extrapolation:
\begin{eqnarray}
u_L^{1D} &=& u_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r u_{\ib-\eb_r}^n, \\
u_R^{1D} &=& u_{\ib} - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r u_{\ib}^n.
\end{eqnarray}
Then we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_r}^{1D} =
\begin{cases}
\half(u_L^{1D} + u_R^{1D}), & \left|w^{\trans}_{\ib-\half\eb_r}\right| < \epsilon \\
u_L^{1D}, & w^{\trans}_{\ib-\half\eb_r} > 0, \\
u_R^{1D}, & w^{\trans}_{\ib-\half\eb_r} < 0. \\
\end{cases}
\end{equation}
Then, we extrapolate the normal velocity to normal faces:
\begin{eqnarray}
u_L &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}\right)\Delta_x u_{\ib-\eb_x}^n + \frac{\dt}{2}f_{\ib-\eb_x} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib-\eb_x+\half\eb_r}^{\trans}+w_{\ib-\eb_x-\half\eb_r}^{\trans}\right)\left(u_{\ib-\eb_x+\half\eb_r}^{1D} - u_{\ib-\eb_x-\half\eb_r}^{1D}\right), \\
u_R &=& u_{\ib}^n + \left(\half - \frac{\dt}{2h}u_{\ib}\right)\Delta_x u_{\ib}^n + \frac{\dt}{2}f_{\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib+\half\eb_r}^{\trans}+w_{\ib-\half\eb_r}^{\trans}\right)\left(u_{\ib+\half\eb_r}^{1D} - u_{\ib-\half\eb_r}^{1D}\right).
\end{eqnarray}
Finally, we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_x}^{\mac} =
\begin{cases}
0, & \left(u_L \le 0 ~ {\rm AND} ~ u_R \ge 0\right) ~ {\rm OR} ~ \left|u_L + u_R\right| < \epsilon, \\
u_L, & u_L + u_R > 0, \\
u_R, & u_L + u_R < 0. 
\end{cases}
\end{equation}

To compute $\wt^{\mac}$, we use an analogous procedure for computing $u^{\mac}$, except that we need to incorporate the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ and $\partial w_0/\partial r$.  But first, we need to compute a time-centered $\wt$ at transverse faces using a 1D Taylor seriex extrapolation:
\begin{eqnarray}
\wt_L^{1D} &=& \wt_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}^n\right)\Delta_x \wt_{\ib-\eb_x}^n, \\
\wt_R^{1D} &=& \wt_{\ib} - \left(\half + \frac{\dt}{2h}u_{\ib}^n\right)\Delta_x \wt_{\ib}^n.
\end{eqnarray}
Then we solve a Riemann problem:
\begin{equation}
\wt_{\ib-\half\eb_x}^{1D} =
\begin{cases}
\half(\wt_L^{1D} + \wt_R^{1D}), & \left|u^{\trans}_{\ib-\half\eb_x}\right| < \epsilon \\
\wt_L^{1D}, & u^{\trans}_{\ib-\half\eb_x} > 0, \\
\wt_R^{1D}, & u^{\trans}_{\ib-\half\eb_x} < 0. \\
\end{cases}
\end{equation}
Then, we extrapolate the normal velocity to normal faces, incorporating the extra term proportional to $w_0$ by using $w$ instead of $\wt$ as the advection velocity and the extra term proportional to $\partial w_0/\partial r$ as a separate term\footnote{The underbraced terms could be replaced by the average of the neighboring $w^{\trans}$.  We still don't know what the best option is.}:
\begin{eqnarray}
\wt_L &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}f_{\ib-\eb_r} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x-\eb_r}^{\trans}+u_{\ib-\half\eb_x-\eb_r}^{\trans}\right)\left(\wt_{\ib+\half\eb_x-\eb_r}^{1D} - \wt_{\ib-\half\eb_x-\eb_r}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\underbrace{\wt_{\ib-\eb_r}}_{?}(w_{0,j-\half} - w_{0,j-\frac{3}{2}}), \\
\wt_R &=& \wt_{\ib}^n + \left(\half - \frac{\dt}{2h}w_{\ib}\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}f_{\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x}^{\trans}+u_{\ib-\half\eb_x}^{\trans}\right)\left(\wt_{\ib+\half\eb_x}^{1D} - \wt_{\ib-\half\eb_x}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\underbrace{\wt_{\ib}}_{?}(w_{0,j+\half} - w_{0,j-\half}).
\end{eqnarray}
Next, we solve a Riemann problem:
\begin{equation}
\wt_{\ib-\half\eb_r}^{\mac} =
\begin{cases}
0, & \left(w_L \le 0 ~ {\rm AND} ~ w_R \ge 0\right) ~ {\rm OR} ~ \left|w_L + w_R\right| < \epsilon, \\
\wt_L, & w_L + w_R > 0, \\
\wt_R, & w_L + w_R < 0. 
\end{cases}
\end{equation}
Finally, we call {\tt addw0} to compute $\Ub^{\mac}$ from $\Ubt^{\mac}$.
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\section{Computing $s^{\edge}$}
\subsection{2D Cartesian Case}
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\section{Computing $\Ub^{\edge}$}
\subsection{2D Cartesian Case}
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\section{Forces}

\cleardoublepage
\begin{table*}
\begin{center}
\caption{Forcing term into make edge scal \newline}
\begin{tabular}{|c|c|c|}
\multicolumn{1}{c}{PRED X}   & \multicolumn{1}{c}{Force} \\
\hline
  &   \\
T $(X)$ & $0$ \\
  &   \\
T $(\rho^\prime)$ & $-\rho^\prime \; \nabla \cdot (\ut+w_0 \er) - \nabla \cdot (\ut \rho_0) $  \\
  &   \\
\hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{H PRED TYPE}   & \multicolumn{1}{c}{Force} \\
\hline
   & \\
 1 $((\rho h)^\prime)$ &  $(\tilde{w} \frac{\partial p_0}{\partial r}) - (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \er) - \nabla \cdot (\ut (\rho h)_0) $  \\
   & \\
 2 $(h)$ & $\frac{1}{\rho} (\psi + \tilde{w} \frac{\partial p_0}{\partial r})$  \\
   & \\
 3 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
 4 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
\hline
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\def\eb    {{\bf e}}
\def\fb    {{\bf f}}
\def\ib    {{\bf i}}
\def\Ub    {{\bf U}}

@@

\section{Computing $\Ubt^{\trans}$}
In {\tt advance\_premac.f90}, we call the function {\tt mkutrans}, which computes the edge-centered transverse velocities, $\Ubt^{\trans}$.  These transverse velocities do not contain $w_0$, so immediately following the call to {\tt mkutrans}, we call {\tt addw0} to compute $\Ub^{\trans}$ from $\Ubt^{\trans}$.  We will only compute the normal component of velocity at each face.\\

@@

For the x-faces, the extrapolation is as follows:
\begin{eqnarray}
u_L &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{h}u_{\ib-\eb_x}^n\right)\Delta_x u_{\ib-\eb_x}^n, \\
u_R &=& u_{\ib}^n - \left(\half + \frac{\dt}{h}u_{\ib}^n\right)\Delta_x u_{\ib}^n.
\end{eqnarray}
We pick the final edge states using a Riemann solver:
\begin{equation}
u^{\trans}_{\ib-\half\eb_x} =
\begin{cases}
0, & (u_L \le 0 ~ {\rm AND} ~ u_R \ge 0) ~ {\rm OR} ~ |u_L + u_R| < \epsilon, \\
u_L, & u_L + u_R > 0, \\
u_R, & u_L + u_R < 0, \\
\end{cases}
\end{equation}
For the radial faces, we must include the radial derivative terms proportional to $w_0$ and $(\Ubt\cdot\eb_r) = \wt$.  The term proportional to $w_0$ is included by using $w$ rather than $\wt$ as the advection speed.  The term proportional to $\wt$ is an additional term:
\begin{eqnarray}
\wt_L &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{h}w_{\ib-\eb_r}^n\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}\wt_{\ib-\eb_r}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib-\eb_r},\label{Radial utrans_L} \\
\wt_R &=& \wt_{\ib}^n + \left(\half - \frac{\dt}{h}w_{\ib}^n\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}\wt_{\ib}^n\left(\frac{\partial w_0}{\partial r}\right)_{\ib}.\label{Radial utrans_R}
\end{eqnarray}
The total radial velocity is defined as:
\begin{equation}
w_{\ib}^n = \wt_{\ib}^n + \frac{w_{0,r+\half}+w_{0,r-\half}}{2}.\label{Total Radial Velocity}
\end{equation}
The spatial derivatives of $w_0$ are given by the two-point centered difference:
\begin{equation}
\left(\frac{\partial w_0}{\partial r}\right)_{\ib} = \frac{w_{0,r+\half}-w_{0,r-\half}}{h}.\label{Radial Derivative of w_0}
\end{equation}
We pick the final edge states using:
\begin{equation}
\wt^{\trans}_{\ib-\half\eb_r} =
\begin{cases}
0, & (w_L \le 0 ~ {\rm AND} ~ w_R \ge 0) ~ {\rm OR} ~ |w_L + w_R| < \epsilon, \\
\wt_L, & w_L + w_R > 0, \\
\wt_R, & w_L + w_R < 0, \\
\end{cases}
\end{equation}
where $w_L = \wt_L + w_{0,r-\half}$ and $w_R = \wt_R + w_{0,r-\half}$.  Finally, we call {\tt addw0} to compute $w^{\trans}$ from $\wt^{\trans}.$
\subsection{3D Cartesian Case}
For the rest of this paper, for 3D Cartesian problems, $\Ub = (u,v,w)$ and $\Ubt = (u,v,\wt)$.  We will use the shorthand $\ib = (i,j,r)$.\\

@@

We first construct $\Ub$ by mapping $w_0$ onto a Cartesian array and adding it to $\Ubt$.  This is a spherical generalization of equation (\ref{Total Radial Velocity}).  We also map $\partial w_0/\partial r$ onto a Cartesian array.  This is a spherical generalization of equation (\ref{Radial Derivative of w_0}).  Then we use an extrapolation analogous to equations equations (\ref{Radial utrans_L}) and (\ref{Radial utrans_R}).  For example, for x-faces:
\begin{eqnarray}
\ut_L &=& \ut_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{h}u_{\ib-\eb_x}^n\right)\Delta_x\ut_{\ib-\eb_x}^n + \frac{\dt}{2}\left[(\Ubt^n\cdot\eb_r)\left(\frac{\partial w_0}{\partial r}\right)(\eb_r\cdot\eb_x)\right]_{\ib-\eb_x}, \\
\ut_R &=& \ut_{\ib}^n + \left(\half - \frac{\dt}{h}u_{\ib}^n\right)\Delta_x\ut_{\ib}^n + \frac{\dt}{2}\left[(\Ubt^n\cdot\eb_r)\left(\frac{\partial w_0}{\partial r}\right)(\eb_r\cdot\eb_x)\right]_{\ib}.
\end{eqnarray}
Then, we use the same Riemann solver as the Cartesian case to obtain $\ut^{\trans}$.  To compute $\vt^{\trans}$ or $\wt^{\trans}$, simply replace all instaces of $\ut$ with $\vt$ (or $\wt$) and all instaces of $x$ with $y$ (or $z$).  Finally, we call {\tt addw0} to compute $\Ub^{\trans}$ from $\Ubt^{\trans}$.
\section{Computing $\Ubt^{\mac,*}$}
In {\tt advance\_premac.f90}, we call {\tt make\_edge\_state} to compute $\Ubt^{\mac,*}$.  We will only compute the normal component of velocity at each face.\\
\subsection{2D Cartesian Case}
To compute $u^{\mac,*}$, first we need to compute a time-centered $u$ at transverse faces using a 1D Taylor series extrapolation:
\begin{eqnarray}
u_L^{1D} &=& u_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}^n\right)\Delta_r u_{\ib-\eb_r}^n, \\
u_R^{1D} &=& u_{\ib} - \left(\half + \frac{\dt}{2h}w_{\ib}^n\right)\Delta_r u_{\ib}^n.
\end{eqnarray}
Then we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_r}^{1D} =
\begin{cases}
\half(u_L^{1D} + u_R^{1D}), & \left|w^{\trans}_{\ib-\half\eb_r}\right| < \epsilon \\
u_L^{1D}, & w^{\trans}_{\ib-\half\eb_r} > 0, \\
u_R^{1D}, & w^{\trans}_{\ib-\half\eb_r} < 0. \\
\end{cases}
\end{equation}
Then, we extrapolate the normal velocity to normal faces:
\begin{eqnarray}
u_L &=& u_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}\right)\Delta_x u_{\ib-\eb_x}^n + \frac{\dt}{2}f_{u,\ib-\eb_x} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib-\eb_x+\half\eb_r}^{\trans}+w_{\ib-\eb_x-\half\eb_r}^{\trans}\right)\left(u_{\ib-\eb_x+\half\eb_r}^{1D} - u_{\ib-\eb_x-\half\eb_r}^{1D}\right), \\
u_R &=& u_{\ib}^n + \left(\half - \frac{\dt}{2h}u_{\ib}\right)\Delta_x u_{\ib}^n + \frac{\dt}{2}f_{u,\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(w_{\ib+\half\eb_r}^{\trans}+w_{\ib-\half\eb_r}^{\trans}\right)\left(u_{\ib+\half\eb_r}^{1D} - u_{\ib-\half\eb_r}^{1D}\right),
\end{eqnarray}
where the force term is given by:\footnote{The code currently does not include the $\pi_0$ term.}
\begin{equation}
\fb =
\left(\begin{array}{c}
f_u \\
f_w \\
\end{array}\right)
= \frac{1}{\rho}\nabla\pi + \frac{1}{\rho_0}\frac{\partial\pi_0}{\partial r}\eb_r - \frac{(\rho-\rho_0)}{\rho}g\eb_r.
\end{equation}
Finally, we solve a Riemann problem:
\begin{equation}
u_{\ib-\half\eb_x}^{\mac,*} =
\begin{cases}
0, & \left(u_L \le 0 ~ {\rm AND} ~ u_R \ge 0\right) ~ {\rm OR} ~ \left|u_L + u_R\right| < \epsilon, \\
u_L, & u_L + u_R > 0, \\
u_R, & u_L + u_R < 0. 
\end{cases}
\end{equation}

To compute $\wt^{\mac,*}$, we use an analogous procedure for computing $u^{\mac,*}$, except that we need to incorporate the terms in equation (\ref{Perturbational Velocity Equation}) proportional to $w_0$ and $\partial w_0/\partial r$.  But first, we need to compute a time-centered $\wt$ at transverse faces using a 1D Taylor series extrapolation:
\begin{eqnarray}
\wt_L^{1D} &=& \wt_{\ib-\eb_x}^n + \left(\half - \frac{\dt}{2h}u_{\ib-\eb_x}^n\right)\Delta_x \wt_{\ib-\eb_x}^n, \\
\wt_R^{1D} &=& \wt_{\ib} - \left(\half + \frac{\dt}{2h}u_{\ib}^n\right)\Delta_x \wt_{\ib}^n.
\end{eqnarray}
Then we solve a Riemann problem:
\begin{equation}
\wt_{\ib-\half\eb_x}^{1D} =
\begin{cases}
\half(\wt_L^{1D} + \wt_R^{1D}), & \left|u^{\trans}_{\ib-\half\eb_x}\right| < \epsilon \\
\wt_L^{1D}, & u^{\trans}_{\ib-\half\eb_x} > 0, \\
\wt_R^{1D}, & u^{\trans}_{\ib-\half\eb_x} < 0. \\
\end{cases}
\end{equation}
Then, we extrapolate the normal velocity to normal faces, incorporating the extra term proportional to $w_0$ by using $w$ instead of $\wt$ as the advection velocity and the extra term proportional to $\partial w_0/\partial r$ as a separate term:\footnote{The underbraced terms could be replaced by the average of the neighboring $w^{\trans}$.  We still don't know what the best option is.}
\begin{eqnarray}
\wt_L &=& \wt_{\ib-\eb_r}^n + \left(\half - \frac{\dt}{2h}w_{\ib-\eb_r}\right)\Delta_r \wt_{\ib-\eb_r}^n + \frac{\dt}{2}f_{w,\ib-\eb_r} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x-\eb_r}^{\trans}+u_{\ib-\half\eb_x-\eb_r}^{\trans}\right)\left(\wt_{\ib+\half\eb_x-\eb_r}^{1D} - \wt_{\ib-\half\eb_x-\eb_r}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\underbrace{\wt_{\ib-\eb_r}}_{?}(w_{0,j-\half} - w_{0,j-\frac{3}{2}}), \\
\wt_R &=& \wt_{\ib}^n + \left(\half - \frac{\dt}{2h}w_{\ib}\right)\Delta_r \wt_{\ib}^n + \frac{\dt}{2}f_{w,\ib} \nonumber \\
&& - \frac{\dt}{4h}\left(u_{\ib+\half\eb_x}^{\trans}+u_{\ib-\half\eb_x}^{\trans}\right)\left(\wt_{\ib+\half\eb_x}^{1D} - \wt_{\ib-\half\eb_x}^{1D}\right) \nonumber \\
&& - \frac{\dt}{2h}\underbrace{\wt_{\ib}}_{?}(w_{0,j+\half} - w_{0,j-\half}).
\end{eqnarray}
Next, we solve a Riemann problem:
\begin{equation}
\wt_{\ib-\half\eb_r}^{\mac,*} =
\begin{cases}
0, & \left(w_L \le 0 ~ {\rm AND} ~ w_R \ge 0\right) ~ {\rm OR} ~ \left|w_L + w_R\right| < \epsilon, \\
\wt_L, & w_L + w_R > 0, \\
\wt_R, & w_L + w_R < 0. 
\end{cases}
\end{equation}
Finally, we call {\tt addw0} to compute $\Ub^{\mac,*}$ from $\Ubt^{\mac,*}$.
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\section{Computing $\rho^{'\edge}, X_k^{\edge}, h^{\edge},$ and $T^{\edge}$}
\subsection{2D Cartesian Case}
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\section{Computing $\Ubt^{\edge}$}
In {\tt velocity\_advance.f90}, we call {\tt make\_edge\_state} to compute $\Ubt^{\edge}$.  Unlike when we computed $\Ubt^{\trans}$ and $\Ubt^{\mac,*}$, we need all components of velocity at each face.
\subsection{2D Cartesian Case}
To 
\subsection{3D Cartesian Case}
\subsection{3D Spherical Case}
\cleardoublepage
\section{Forces}
\begin{table*}
\begin{center}
\caption{Forcing term into make edge scal \newline}
\begin{tabular}{|c|c|c|}
\multicolumn{1}{c}{PRED X}   & \multicolumn{1}{c}{Force} \\
\hline
  &   \\
T $(X)$ & $0$ \\
  &   \\
T $(\rho^\prime)$ & $-\rho^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut \rho_0) $  \\
  &   \\
\hline
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{|c|c|}
\multicolumn{1}{c}{H PRED TYPE}   & \multicolumn{1}{c}{Force} \\
\hline
   & \\
 1 $((\rho h)^\prime)$ &  $(\tilde{w} \frac{\partial p_0}{\partial r}) - (\rho h)^\prime \; \nabla \cdot (\ut+w_0 \eb_r) - \nabla \cdot (\ut (\rho h)_0) $  \\
   & \\
 2 $(h)$ & $\frac{1}{\rho} (\psi + \tilde{w} \frac{\partial p_0}{\partial r})$  \\
   & \\
 3 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
 4 $(T)$ & $\frac{1}{\rho c_p} \left[ (1 - \rho h_p) (\psi + \tilde{w} \frac{\partial p_0}{\partial r}) \right]$ \\
   & \\
\hline
\hline
\end{tabular}
\end{center}
\end{table*}
